How the News Media Shapes Public Opinion

### 2022-06-28 pres/20211014/TADA_20211014.Rmd
Update pres as well
pray

---
title: "The effect of changing news frames"
subtitle: "Presentation at the 2021 Annual Conference of the Political Studies Association of Ireland"
author: "Nicolai Berk$^*$"
institute: "$^*$RTG Dynamics/Humboldt Universität zu Berlin"
date: "Oct 9th, 2021"
output: 
  beamer_presentation:
    theme: "Frankfurt"
    # colortheme: "lily"
    # fonttheme: "professionalfonts"
    slide_level: 2
    toc: False
header-includes:
# - \usepackage{fontawesome}
- \AtBeginSection{}
bibliography: PhD-Proposal.bib
---

@@

- Many current approaches test media effects of different outlets [@Gentzkow2011; @Guess2021].
- However, **news consumers discount bias and take cues from outlets**.
  + @Baum2008 show that consumers take heuristics about content bias from outlet brands.
  + @Chiang2011a show that outlet bias moderates the effect of candidate endorsements.

$\rightarrow$ **within-outlet changes** in content most likely cases to observe media effects.

@@

- I draw on literature on 
  + the **value-expectancy** framework [@Ajzen2000].
  + and **emphasis framing** [@Leeper2020; @Nelson1997].
- Argues that issue attitudes are a product of **associated considerations**.

@@

**Topics**:

>>>>

---
title: "The effect of changing news frames"
author: "Nicolai Berk$^*$"
institute: "$^*$RTG Dynamics/Humboldt Universität zu Berlin"
date: "Oct 14th, 2021"
output: 
  beamer_presentation:
    theme: "Frankfurt"
    # colortheme: "lily"
    # fonttheme: "professionalfonts"
    slide_level: 2
    toc: False
header-includes:
# - \usepackage{fontawesome}
- \AtBeginSection{}
bibliography: PhD-Proposal.bib
---

@@

- Many current approaches test media effects of different outlets [@Gentzkow2011; @Guess2021].
- However, \alert{news consumers discount bias and take cues from outlets}.
  + @Baum2008 show that consumers take heuristics about content bias from outlet brands.
  + @Chiang2011a show that outlet bias moderates the effect of candidate endorsements.

$\rightarrow$ \alert{within-outlet changes} in content most likely cases to observe media effects.

@@

- I draw on literature on 
  + the \alert{value-expectancy} framework [@Ajzen2000].
  + and \alert{emphasis framing} [@Leeper2020; @Nelson1997].
- Argues that issue attitudes are a product of \alert{associated considerations}.

@@

\alert{Topics}:

### 2022-06-28 pres/20211028/EPSIP_20211028.Rmd
Update pres as well
pray

![](vis/volksempfanger.jpg){width=40%}

@@

- Panel data from the German Longitudinal Election Study [@GLES2019LongTermTracking].
- Contains questions on news consumption and immigration and integration attitudes.
- 6 waves in 2017, containing both items.
- Immigration attitude measured on a 7-point Likert scale:
  + "*Immigration should be made easier (-3) or restricted (3)*".

@@

- Capital crime (sexual assault/rape/murder) committed by refugees,
- illegal entry and petty crime,
- refugee numbers,
- labour market needs for and job market integration of refugees,
- deportations,
- internment camps (e.g. Moria),
- drownings in the Mediterranean.

@@

## Preliminary conclusion

- No effects of media framing even in most-likely case.
- *However*, many possible explanations:
  + Measurement issues,
  + Issue-sorting in 2015, subsequent "digging in",
  + too little variation in dependent.

@@

## Further hypotheses

- Motivated reasoning and polarisation [@Taber2006].
- Readers respond by changing outlet [@Arceneaux2013].
- Mobilisation, not attitudinal change [@Gentzkow2011; @Stetka2020].

## To-do's up next

- Clump frames together for holistic picture.
- Estimate effect on readership, attitude polarisation, and AfD-support.
- Natural experiment (again)?

@@

>>>>

![](vis/volksempfanger.jpg){width=30%} 
![](vis/bild_umgebracht_asyl.jpeg){width=60%}

@@

- Panel data from the German Longitudinal Election Study [@GLES2019LongTermTracking].
- Contains questions on news consumption, immigration and integration attitudes, as well as party preference.
- Dependent variables:
  + Immigration attitude (7-point scale).
  + Integration attitude (7-point scale).
  + Attitude toward AfD (11-point scale).

@@

- Capital/sexual crime committed by refugees,
- general crime,
- refugee numbers,
- labour market needs for and job market integration of refugees,
- deportations,
- internment camps (e.g. Moria),
- drownings in the Mediterranean.

@@

## Preliminary conclusion {.allowframebreaks}

\begin{center}

\textbf{No effects of media framing even when considering within-outlet changes.}

\end{center}

However, other possible explanations:

- Issue-sorting in 2015, subsequent "digging in",
- Measurement issues (esp. news exposure).

@@

## Next steps (possibly paper #2)

### Theoretical additions:

- Test if readers respond by **stopping to read newspaper** [@Arceneaux2013; @Chiang2011a].
- Assess **issue sorting** [@Carmines1986] across time.

### Empirical additions:

- (Alternative measure of association: diachronic embeddings? embedding topic model?)
- (Back to natural experiment?)
- (More cases?)

@@

## Potential natural experiment

![](vis/frames_bild_diekmann_pres.png)

### 2022-06-28 pres/20220401/UNDA.Rmd
Update pres as well
pray

---
title: "Emphasis Framing in the Real World"
subtitle: "Migration, Crime and the Heterogenous Impact of Media Content"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
    includes:
      after_body: insert-logo.html
---

@@

>>>>

---
title: "Learning what's at Stake"
subtitle: "How the News Media Shapes Public Opinion by Defining Political Issues"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
    includes:
      after_body: insert-logo.html
---

@@

# 1000 Bootstraps

```{r, out.width= "90%"}

gles_p_long_1617$dv <- gles_p_long_1617$`1130_clean`
gles_p_long_1617$treat <- gles_p_long_1617$bild_init
gles_p_long_1617$post <- gles_p_long_1617$date_clean>= as.Date("2017-02-01")

points <- ate$coefficients
ests <- cbind(points, confint(ate))

load('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/did_bootstraps.RData')

direct <- coef(inter)["postTRUE:treatTRUE"]
interact <- coef(inter)["postTRUE:treatTRUE:init_mig"]

did_bootstrap <- 
  ggplot() +
  geom_histogram(data = gles_p_long_1617 %>% filter(wave == "1"), mapping = aes(x = init_mig, after_stat(density)), alpha = 0.4, bins = 8) +
  geom_abline(data = bs_did_ests, aes(slope = IA, intercept = DiD, group = boots), alpha= 0.05) +
  geom_abline(slope = interact, intercept = direct, col = "red") +
  theme_minimal() +
  geom_hline(yintercept = 0, col = "black") +
  scale_x_continuous(limits=c(-3,3)) +
  scale_y_continuous(limits=c(0,.6)) +
  ggtitle(paste0(B, " bootstrap estimates of heterogenous treatment effect")) +
  ylab("Estimate") + xlab("Initial migration attitude")

### 2022-06-28 pres/20220506/Dublin.Rmd
Update pres as well
pray

@@

Presentation prepared for the 13th European Graduate Network Conference at the European University Institute, Florence

@@

knitr::include_graphics("firenze_intro_ukraine.png")

@@

knitr::include_graphics("firenze_crime.png")

@@

- **everyday, medium-term** impact?
- Which news **content** is effective?
- Effect dependent on individual **predispositions**?

@@

1. News media influences public opinion by __emphasising certain considerations__ over others.
3. **Predispositions** structure individual susceptibility.

@@

## Accessibility

@@

- Experimental research suggests **exposure to consideration mutes effect** of subsequent exposure `r Citep(myBib[c("Druckman2012")])`.
- Hence media content only affects opinions when exposed individual **learns something new**.

@@

#### Independent Variable `r Citep(myBib["Nicholson2020"], before = "partly following ")`

- Collected 2.5M news articles from major German daily newspapers.
- Two-step identification of issue definitions:
  1. Supervised deep-learning model (BERT) to **select migration content**
  2. Structural Topic Model to **identify considerations**

@@

## visualise
trendplot <- 
  merged_media %>% 
  filter(date_new < as.Date("2018-01-01"), date_new >= as.Date("2016-01-01")) %>% 
  mutate(
    date_month = floor_date(as.Date(date_new), 'month')
  ) %>%
  group_by(paper != "Bild", date_month) %>%
  summarise(across(share_mig:hungary_referendum_share, mean, na.rm = T),
            across(n_mig_sal:n_tot, sum, na.rm = T)) %>%
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         post = date_month >= as.Date("2017-02-01")) %>% 
  filter(date_month < as.Date("2020-01-01")) %>% 
  ggplot(aes(x = date_month, y = crime_share, col = `paper != "Bild"`)) +
  geom_line(size = 2) +
  geom_rug(data = survey_dates, aes(x = date),sides = 't', inherit.aes = F, size = 2) +
  # geom_point() +
  # geom_smooth(alpha = 0.1) +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red", size = 2) +
  # ggtitle("Monthly Share of Migration Content Devoted to Crime Frames", "Bild vs. other major daily newspapers, 2016-2017") + 
  xlab("") + ylab("Share of Migration Content") +
  # facet_wrap(~paper)
  # theme(legend.position = "none") +
  theme_xaringan() + 
  scale_color_discrete(name = "Bild reader", labels = c("Yes", "No"))

@@

## Measurement: News Consumption

#### Conditioning Variable

- Question on newspapers consumed last week.
- Simple binary variable for DiD-model.
- Calculate share of migration content devoted to crime for FE model.

## Measurement: Accessibility

#### Moderator

- **Initial migration opinion** reflects product of weighted considerations.
- Those with **liberal migration attitudes** are **less likely to hold crime considerations**.

@@

plot_did_ate <- bs_inter_vis(gles_p_long_1617, size = 2, col = "#004A95")  + theme_xaringan()
plot_did_inter <- bs_inter_vis(gles_p_long_1617, size = 2, col = "#004A95") + theme_xaringan()

@@

## Conditioning on Accessibility

@@

DiD_bs(gles_p_long_1617) +
  theme_xaringan()

@@

DiD_groups(gles_p_long_1617) +
  theme_xaringan()

@@

@@

- **ATE is null** when not moderating with prior attitude.
- **Conservatives do not react** to increased crime framing.
- Is this a ceiling effect? No, because:
  - results hold when comparing among conservative outlets
  - Conservatives react to other frames (ISIS, cues by party elites)

# Conclusion

- Media **content affects attitude** formation.
- **Effect is conditional** on pre-existing attitude.

## $\rightarrow$ Attitude is a **product of information and predisposition** `r Citep(myBib["Zaller1992"])`.

@@

- how important these effects are in **more fragmented media landscapes**,
- which content affects **which groups**,
- which **other actors** can affect framing in the media.

@@

## Identify Migration Content

- Annotate 1800 articles to identify their migration content.
- Fine-tune German BERT deep-learning classifier.
- accuracy: 95.5% (F1: 0.94, recall: 0.93, precision: 0.95)
- 13.5k out of 400k articles in 2017 about migration (3.5\%)

## Measure Considerations about Migration

- Estimate 60-topic structural topic model on identified migration articles `r Citep(myBib["Roberts2014"])`.
- using date and paper as covariates `r Citep(myBib["Nicolls2020"])`.
- Annotate.
- Select crime-related considerations.

>>>>

# Framing Effects in the Wild

@@

Presentation prepared for the 4th Annual CompText Conference, Dublin

@@

```{r out.width="80%"}

knitr::include_graphics("collage_ukraine.png")

@@

```{r, out.width='100%'}

knitr::include_graphics("collage.png")

@@

- Which news **content** is effective?
- **Everyday, medium-term** impact?
- Effect dependent on individual **predispositions**?

@@

1. News media influences public opinion by __emphasising certain considerations__ over others.
2. **Predispositions** structure individual susceptibility.

@@

## Availability

@@

- Experimental research suggests that **holding a consideration in mind decreases susceptibility to framing** `r Citep(myBib[c("Druckman2012")])`.
- Hence media content only affects opinions when exposed individual **learns something new**.

@@

#### Independent Variable

- Collected 2.5M news articles from major German daily newspapers.
- Two-step identification of issue definitions:
  1. Supervised deep-learning model (BERT) to **select migration content**.
  2. Structural Topic Model to **identify considerations**.

# Identifying migration content

#### Problem: migration content is rare

### Solution: oversample migration content

1. Define **seed dictionary** of migration terms.
2. Extend dictionary using word embeddings.
3. Oversample from articles mentioning immigration terms.

# Identifying migration content II

- RA annotates 1800 articles.
- Fine-tune **German BERT** to identify migration content (accuracy 0.96, F1: 0.94, recall: 0.93, precision: 0.95).
- Predict label for 2.5M news articles: 90,000 about migration.

# Identifying Considerations about Immigration `r Citep(myBib["Nicholson2020"], before = "following ")`

- Apply **STM** with 60 topics `r Citep(myBib["Roberts2014"])` to identify migration frames.
- **Annotate** all topics, **select** the ones about crime.
- Estimate daily prevalence for each newspaper.

@@

## visualise
trendplot <- 
  merged_media %>% 
  filter(date_new < as.Date("2018-01-01"), date_new >= as.Date("2016-01-01")) %>% 
  mutate(
    date_month = floor_date(as.Date(date_new), 'month')
  ) %>%
  group_by(paper != "Bild", date_month) %>%
  summarise(across(share_mig:hungary_referendum_share, mean, na.rm = T),
            across(n_mig_sal:n_tot, sum, na.rm = T)) %>%
  mutate(crime_share = crime_schlepp_share + sexual_assault_share,
         post = date_month >= as.Date("2017-02-01")) %>% 
  filter(date_month < as.Date("2020-01-01")) %>% 
  ggplot(aes(x = date_month, y = crime_share, col = `paper != "Bild"`)) +
  geom_line(size = 2) +
  geom_rug(data = survey_dates, aes(x = date),sides = 't', inherit.aes = F, size = 2) +
  # geom_point() +
  # geom_smooth(alpha = 0.1) +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red", size = 2) +
  # ggtitle("Monthly Share of Migration Content Devoted to Crime Frames", "Bild vs. other major daily newspapers, 2016-2017") + 
  xlab("") + ylab("Share of Migration Content") +
  # facet_wrap(~paper)
  # theme(legend.position = "none") +
  theme_xaringan() + 
  scale_color_discrete(name = "Outlet", labels = c("Bild", "Other"))

@@

## Measurement: News Consumption and Availability

#### Exposure to Treatment

- Question on newspapers consumed last week.
- Simple binary variable indicating *Bild* consumption.
- Alternative: Calculate individual exposure to crime framing.

--

#### Availability

- **Initial migration opinion**.
- Reporting **migrant crime as MIP**.

@@

gles_p_long <- fread('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/gles/Panel/long_cleaned.csv')

set.seed(42)
B <- 1000

## no resampling
gles_p_long <- 
  gles_p_long %>% 
  select(lfdn, date_clean, `1130_clean`, wave) %>% 
  filter(!is.na(`1130_clean`), wave == "1") %>% 
  mutate(init_mig = `1130_clean`) %>% 
  select(lfdn, init_mig) %>% 
  right_join(gles_p_long, by = "lfdn")

## with resampling
## still need to think about implications of this
gles_p_long <-
  gles_p_long %>%
  select(lfdn, date_clean, `1130_clean`) %>%
  filter(!is.na(`1130_clean`)) %>%
  arrange(lfdn, date_clean) %>%
  group_by(lfdn) %>%
  slice(1) %>%
  mutate(init_mig_res = `1130_clean`) %>%
  select(lfdn, init_mig_res) %>%
  right_join(gles_p_long, by = "lfdn")

gles_p_long <- 
  gles_p_long %>% 
  mutate(mip_mig_crime_lag = lag(mip_mig_crime)) %>% 
  filter(!is.na(mip_mig_crime)) %>% 
  arrange(lfdn, date_clean) %>% 
  group_by(lfdn) %>% 
  filter(wave == "1") %>% 
  mutate(mip_mig_crime_init = mip_mig_crime) %>% 
  select(lfdn, mip_mig_crime_init) %>% 
  right_join(gles_p_long, by = "lfdn")

gles_p_long <- 
  gles_p_long %>% 
  filter(wave == "1") %>% 
  mutate(bild_init = ifelse(is.na(`1661a_clean`), NA, `1661a_clean` > 0)) %>% 
  select(bild_init, lfdn) %>% 
  right_join(gles_p_long, by = "lfdn")

gles_p_long <- 
  gles_p_long %>% 
  arrange(lfdn, date_clean) %>% 
  group_by(lfdn) %>% 
  slice(1) %>% 
  mutate(treat_alt = ifelse(is.na(`1661a_clean`), NA, `1661a_clean` > 0)) %>% 
  select(treat_alt, lfdn) %>% 
  right_join(gles_p_long, by = "lfdn")

## vis dv by treatment group and conditioning var

did_desc_plot <- 
  gles_p_long %>%
  filter(date_clean < as.Date("2018-01-01")) %>% 
  filter(!is.na(`1130_clean`) & !is.na(bild_init)) %>% 
  mutate(init_mig_cat = 
           case_when(
             init_mig > 0 ~ "01 - Conservative",
             init_mig == 0 ~ "02 - Neutral",
             init_mig < 0 ~ "03 - Liberal"
           )) %>% 
  group_by(bild_init, wave, init_mig) %>% 
  select(`1130_clean`, date_clean) %>% 
  summarise(dv = mean(`1130_clean`, na.rm = T),
            dv_sd = sd(`1130_clean`, na.rm = T),
            date_min = min(date_clean, na.rm = T),
            n_resps = n()) %>%
  mutate(
    lower = dv + qt(0.025, n_resps - 1) * (dv_sd/sqrt(n_resps)),
    upper = dv + qt(0.975, n_resps - 1) * (dv_sd/sqrt(n_resps))
  ) %>% 
  ggplot(aes(date_min, dv, ymin = lower, ymax = upper, col = !bild_init, fill = !bild_init)) +
  geom_line() +
  geom_ribbon(alpha = 0.5) +
  geom_vline(xintercept = as.Date("2017-02-01"), lty = 2, col = "red") +
  facet_grid(~init_mig) +
  ggtitle("Average migration opinion dependent on initial migration opinion", 
          "Bild vs. other major daily newspapers, 2016-2017") + 
  xlab("Date") + ylab("Migration Opinion") +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/paper/vis/did_descriptive.svg",
       did_desc_plot,
       device = "svg", width = 10, height = 6)

gles_p_long_1617 <- 
  gles_p_long %>% 
        filter(date_clean >= as.Date("2016-01-01"),
               date_clean <  as.Date("2018-01-01"))

gles_p_long_1617$dv <- gles_p_long_1617$`1130_clean`
gles_p_long_1617$treat <- gles_p_long_1617$bild_init
gles_p_long_1617$post <- gles_p_long_1617$date_clean>= as.Date("2017-02-01")

# model 1: direct effect
ate <- 
  feglm(dv ~ post * treat, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

inter <- 
  feglm(dv ~ post * treat * init_mig, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

points <- ate$coefficients
ests <- cbind(points, confint(ate))

plot_did_ate <- 
  ests %>%
  filter(row.names(.) == "postTRUE:treatTRUE") %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange(size = 2) +
  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
  ylab("") + xlab("Estimate") +
  xlim(-0.1, 0.3) + 
  scale_y_discrete(labels = rev(c("DiD"))) +
  ggtitle("Average treatment effect") + 
  theme_xaringan()

plot_did_inter <- 
  ests %>% 
  filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:init_mig")) %>% 
  mutate(name = fct_reorder(row.names(.), desc(row.names(.)))) %>% 
  ggplot(aes(y = name, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange(size = 2) +
  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("DiD-estimate with interaction") +
  xlim(-0.1, 0.3) + 
  scale_y_discrete(labels = rev(c("DiD", "DiD X Initial Opinion"))) +
  ggtitle("Heterogenous treatment effects") + 
  theme_xaringan()

did_groups <- 
  gles_p_long_1617 %>% 
  filter(!is.na(treat), !is.na(init_mig)) %>%
  group_by(treat, post, init_mig) %>% 
  summarise(
    dv_point = mean(dv, na.rm = T)
    ) %>% 
  filter(post) %>% 
  pivot_wider(
    names_from = treat,
    values_from = dv_point
  ) %>% 
  mutate(difference = `TRUE` - `FALSE`) %>% 
  ggplot(aes(x = init_mig, y = difference)) +
  geom_col() + 
  theme_xaringan() + xlab("") + ylab("") +
  ggtitle("Effect across initial migration attitude")

load('C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/data/did_bootstraps.RData')

direct <- coef(inter)["postTRUE:treatTRUE"]
interact <- coef(inter)["postTRUE:treatTRUE:init_mig"]

did_bootstrap <- 
  ggplot() +
  geom_histogram(data = gles_p_long_1617 %>% filter(wave == "1"), mapping = aes(x = init_mig, after_stat(density)), alpha = 0.4, bins = 8) +
  geom_abline(data = bs_did_ests, aes(slope = IA, intercept = DiD, group = boots), alpha= 0.05) +
  geom_abline(slope = interact, intercept = direct, col = "red") +
  geom_hline(yintercept = 0, col = "black") +
  scale_x_continuous(limits=c(-3,3)) +
  scale_y_continuous(limits=c(0,.6)) +
  ggtitle(paste0(B, " bootstrap estimates of heterogenous treatment effect")) +
  ylab("Estimate") + xlab("Initial migration attitude") +
  theme_xaringan()

ggsave(plot = did_bootstrap,
       filename = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild/paper/vis/DiDXinit_imm.svg', device = "svg")

plot_did_ate / plot_did_inter

@@

## Conditioning on Availability

@@

did_bootstrap

@@

did_groups

@@

# Moderator: MIP

# DiD
# model 1: direct effect
ate <- 
  feglm(dv ~ post * treat, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

inter <- 
  feglm(dv ~ post * treat * mip_mig_crime_init, 
      cluster = c("lfdn"), 
      data = gles_p_long_1617)

points <- ate$coefficients
ests <- cbind(points, confint(ate))

plot_did_ate <- 
  ests %>%
  filter(row.names(.) == "postTRUE:treatTRUE") %>% 
  ggplot(aes(y = row.names(.), x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange(size = 2) +
  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
  ylab("") + xlab("Estimate") +
  scale_y_discrete(labels = rev(c("DiD"))) +
  ggtitle("Average treatment effect") + 
  theme_xaringan()

plot_did_inter <- 
  ests %>% 
  filter(row.names(.) %in% c("postTRUE:treatTRUE", "postTRUE:treatTRUE:mip_mig_crime_initTRUE")) %>% 
  mutate(name = fct_reorder(row.names(.), desc(row.names(.)))) %>% 
  ggplot(aes(y = name, x = points, xmin = `2.5 %`, xmax = `97.5 %`)) +
  geom_pointrange(size = 2) +
  geom_vline(xintercept = 0, col = "red", lty = 2, size = 2) +
  ylab("") + xlab("Estimate") +
  ggtitle("DiD-estimate with interaction") +
  scale_y_discrete(labels = rev(c("DiD", "DiD X Initial Opinion"))) +
  ggtitle("Heterogenous treatment effects") + 
  theme_xaringan()

@@

- Media **content affects attitude** formation.
- **ATE is null** when not moderating with prior attitude.
- Effect conditioned by **Prior availability** of consideration.

### $\rightarrow$ Attitude is a **product of information and predisposition** `r Citep(myBib["Zaller1992"])`.

@@

- How important are these effects in **more fragmented media landscapes**?
- Which content affects **which groups**?
- Which **other actors** can affect framing in the media?

@@
